---
title: "p8105_hw3_zy2378"
author: "zy"
date: "10/18/2021"
output: github_document
---

```{r}
library(p8105.datasets)
library(tidyverse)
library(dplyr)
library(ggplot2)
data("instacart")
data("brfss_smart2010")
instacart
brfss_smart2010
```

## Data Description
The Instacart data contains observations on `r nrow(instacart)` orders from instacart store online. The data include `r ncol(instacart)` variables, and are the characteristics of the orders and the product，including product name, product id, order name, etc.
For observation at row1, the order is id is 1, and product id is 49302, the order that the product was add to chart is 1, and it have been ordered before by this customer. The user id is 112108, and the order belongs to the train evaluation set. The order number for this user is 4, and the order was placed on Thursday 10am. It have been 9 days since this user's last order, and the product is Bulgarian Yogurt. The aisle id is 120, and the product belongs to the yogurt aisle. The department id is 16, and is dairy eggs.

##Problem 1

```{r}
aisle_df1=
  instacart%>%
  group_by(aisle)%>%
  summarize(n_obs=n())%>%
  mutate(rank=rank(n_obs))
aisle_df1

aisle_df2=
  aisle_df1%>%
  filter(n_obs>=10000)%>%
  select(-rank)
aisle_df2


ggplot(aisle_df2,aes(x=aisle,y=n_obs))+
  geom_point()+
  theme(axis.text.x=element_text(angle=90))+
  labs(
    title = "Number of items ordered in each aisle",
    x = "aisle",
    y = "number of items ordered")



```

1.There are 134 aisles, and the most items that ordered from is the fresh vagetables aisle.

```{r}
baking_ingredients_df=
  instacart%>%
  filter(aisle=="baking ingredients")%>%
  group_by(product_name)%>%
  summarize(n_obs=n())%>%
  mutate(rank=rank(n_obs))%>%
  filter(rank>=521)%>%
  select(-rank)%>%
  mutate(aisle=c("baking ingredients","baking ingredients","baking ingredients"))%>%
  select(aisle,product_name,n_obs)
baking_ingredients_df

dog_food_care_df=
  instacart%>%
  filter(aisle=="dog food care")%>%
  group_by(product_name)%>%
  summarize(n_obs=n())%>%
  mutate(rank=rank(n_obs))%>%
  filter(rank>=353)%>%
  select(-rank)%>%
  mutate(aisle=c("dog food care","dog food care","dog food care"))%>%
  select(aisle,product_name,n_obs)
dog_food_care_df

packaged_vegetables_fruits_df=
  instacart%>%
  filter(aisle=="packaged vegetables fruits")%>%
  group_by(product_name)%>%
  summarize(n_obs=n())%>%
  mutate(rank=rank(n_obs))%>%
  filter(rank>=564)%>%
  select(-rank)%>%
  mutate(aisle=c("packaged vegetables fruits","packaged vegetables fruits","packaged vegetables fruits"))%>%
  select(aisle,product_name,n_obs)
packaged_vegetables_fruits_df

bind_rows(baking_ingredients_df,dog_food_care_df,packaged_vegetables_fruits_df)




```
2.The three most popular items in the baking ingredients aisle is `r baking_ingredients_df$product_name`, in the dog food care aisle is `r dog_food_care_df$product_name`, and in the packaged vegetables fruits aisle is `r packaged_vegetables_fruits_df$product_name`.

```{r}
pink_lady_apples_df=
  instacart%>%
  filter(product_name=="Pink Lady Apples")%>%
  select(product_name,order_dow,order_hour_of_day)%>%
  group_by(order_dow)%>%
  summarize(mean=mean(order_hour_of_day))%>%
  mutate(product_name=rep("Pink Lady Apples",7))%>%
  select(product_name,order_dow,mean)
pink_lady_apples_df

coffee_ice_cream_df=
  instacart%>%
  filter(product_name=="Coffee Ice Cream")%>%
  select(product_name,order_dow,order_hour_of_day)%>%
  group_by(order_dow)%>%
  summarize(mean=mean(order_hour_of_day))%>%  
  mutate(product_name=rep("Coffee Ice Cream",7))%>%
  select(product_name,order_dow,mean)
coffee_ice_cream_df

df_mean_order_hour_of_day=
  bind_rows(pink_lady_apples_df,coffee_ice_cream_df)%>%
  pivot_wider(names_from = order_dow,values_from=mean)%>%
  rename("Sunday"="0","Monday"="1","Tuesday"="2","Wednesday"="3","Thursday"="4","Friday"="5","Saturday"="6")
df_mean_order_hour_of_day
```
3. The table shows the average order hour of the day for Pink Lady Apples	and Coffee Ice Cream on each day of a week. For example, the average order hour of the day for Pink Lady Apples is 13.44118	on Sunday.

##Problem 2

```{r}
brfss_df=
  brfss_smart2010%>%
  janitor::clean_names()%>%
  filter(topic=="Overall Health")%>%
  filter(response%in%c("Poor","Fair","Good","Very good","Excellent"))%>%
  mutate(response=factor(response,levels=c("Poor","Fair","Good","Very good","Excellent")))

brfss_2002_df=
  brfss_df%>%
  filter(year=="2002")%>%
  group_by(locationabbr,locationdesc)%>%
  summarize(n_obs=n())%>%
  group_by(locationabbr)%>%
  summarize(n_obs1=n())%>%
  filter(n_obs1>=7)

brfss_2010_df=
  brfss_df%>%
  filter(year=="2010")%>%
  group_by(locationabbr,locationdesc)%>%
  summarize(n_obs=n())%>%
  group_by(locationabbr)%>%
  summarize(n_obs1=n())%>%
  filter(n_obs1>=7)

brfss_df
brfss_2002_df
brfss_2010_df

```

1. In 2002,`r brfss_2002_df$locationabbr` were observed at 7 or more locations.In 2010,`r brfss_2010_df$locationabbr` were observed at 7 or more locations.

```{r}
brfss_excellent_df=
  brfss_df%>%
  filter(response=="Excellent")%>%
  select(year,locationabbr,data_value)%>%
  drop_na()%>%
  group_by(locationabbr,year)%>%
  summarize(average_data_value=mean(data_value))
brfss_excellent_df
ggplot(brfss_excellent_df,aes(x=year,y=average_data_value,group=locationabbr,color=locationabbr))+
  geom_point()+
  geom_line()+
  labs(
    title="Average Data Value From 2002 to 2010",
    x="year",
    y="Average Data Value"
  )

```

2.The dataset have 433 rows and 3 columns, variable names are `r names(brfss_excellent_df)`.

```{r}
brfss_data_value_df=
  brfss_df%>%
  filter(year%in%c("2006","2010"))%>%
  filter(locationabbr=="NY")
brfss_data_value_df
ggplot(brfss_data_value_df,aes(x=response,y=data_value,color=year))+
  geom_point(alpha = .3) +
  geom_smooth(se = FALSE) + 
  facet_grid(. ~ year)
  
```

3.The dataset have 75 rows and 23 columns, which contains 45 observations for the year 2010, and 30 observations for the year 2006.

##Problem 3
```{r,fig.width = 6,fig.asp = .6}
accel_df=
  readr::read_csv("./data/accel_data.csv")%>%
  janitor::clean_names()%>%
  mutate(weekday_vs_weekend=ifelse(day%in%c("Saturday","Sunday"),"weekend","weekday"))%>%
  mutate(day=factor(day,levels=c("Monday","Tuesday","Wednesday","Thursday","Friday","Saturday","Sunday")))%>%
  mutate(weekday_vs_weekend=factor(weekday_vs_weekend,levels=c("weekend","weekday")))
accel_df

accel_df1=
  accel_df%>%
  pivot_longer(activity_1:activity_1440,names_to = "activity",names_prefix = "activity_",values_to="value")
accel_df1
accel_total_df=
  accel_df1%>%
  group_by(week,day_id,day,weekday_vs_weekend)%>%
  summarize(activity_total=sum(value))
ggplot(accel_total_df,aes(x=day_id,y=activity_total))+
  geom_point()+
  geom_line()+
  labs(
    title="total activity value for each day",
    x="day",
    y="activity value"
  )
accel_total_df


ggplot(accel_df1,aes(x=activity,y=value,group=day_id))+
  geom_point(aes(color=week))+
  scale_x_discrete(
    breaks=c(1,350,900),
    labels=c("activity_1","activity_350","activity_900")
  )+
  labs(
    title="24-hour activity for each day",
    x="activity",
    y="activity value"
  )
  
```

1. The tidied dataset have week, day_id, day, weekday_vs_weekend, and activity variables on each minute of a 24-hour day starting at midnight.The dataset have 35 observations, and have overall 1444 variables.
2. There are not apparent trend for the total activity for each day, but the fluctuation is large beginning from day 22.
3.The activity value for each minute tend to go down as weeks pass from week 1 to week 5.

##

